A data-driven, pixel-level model to improve the precision of \Kepler\ photometry

### 2013-10-13 documents/plm.tex
causal structure

First idea: data modeled with data... huge models, regularization...

Second idea: causality restricts the choice of data to use...

>>>>

[General formula here for a pixel predicted using a linear combination of other pixels.
  And the objective function, generally?]

The second general idea about data-driven modeling is the investigator's beliefs
  about the causal processes that generate the data
  are crucial in restricting the kinds of data that can be used as input to the model.
That is, different assumptions about the physical properties of the data
  and the data-taking system
  lead to different structures for the data-driven model.
For example, in the case of \Kepler\ data,
  if we believe that different stars in the \Kepler\ field vary independently
  (that is, are not physically synchronized in any way),
  then the only reason that one star might show variability that is \emph{predictive}
  (useful for prediction) of another star's variability
  is that both stars are being observed by the same device or spacecraft.
That is, one star's pixels can be used to predict another star's pixels
  inasmuch as spacecraft issues imprint on both stars in related ways;
  they share a common cause.
For another example, if we think the spacecraft is being affected by
  processes that take place over time-scales longer than a single read-out
  (for example, thermal processes),
  then it would be sensible to model the data at time $t$ using not just simultaneous data,
  but also data from a range of times around $t$.
For another example, if an investigator doesn't care about preserving stellar variability,
  and just wants to detect exoplanet transits (say),
  pixels from the target star can be used to predict pixels from the target star,
  provided they are at large-enough time lags that they don't overlap (in time)
  the signals of interest.
That is, if the model is designed to fit not just spacecraft variability
  but also intrinsic stellar variability,
  the predictive model will be permitted to use as input pixels that \emph{do} overlap the target star.
In what follows, we are only going to use input data that do not overlap that target star pixels.
These models ought to remove spacecraft variability but not intrinsic stellar variability.
